Governing through patronage: the bargain for education in decentralized Brazil

### 2020-10-01 paper/paper.tex
redraft intro

Across the world, vulnerable populations rely on governments for access to basic public services such as education. In the developing world, the quality of public education remains low: functional illiteracy is widespread, basic mathematical operations beyond the reach of most. This ``learning poverty'' is in  How can local governments improve the quality the of public services they deliver? In particular, how do political actors reshape bureaucratic institutions, and what are their downstream consequences for student learning.

>>>>

Across the world, vulnerable populations rely on governments for access to basic public services such as education. In the developing world, the quality of public education remains low: functional illiteracy is widespread, basic mathematical operations beyond the reach of most. The World Bank refers to as ``learning poverty'': low gains from education even when access to a public school exists, in contrast with earlier focus on access to education.\footnote{For more information, see \hyperlink{here}{https://www.worldbank.org/en/topic/education/brief/learning-poverty}.} These outcomes stem from an institutional cascade: political institutions shape the street-level bureaucracies responsible for providing these educational services.

How can local governments improve the quality the of public services they deliver? In particular, how do political actors reshape bureaucratic institutions, and what are their downstream consequences for student learning.
